Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex

For each program and each pair $(D_1,D_2)$ of abstract domains, we compare by
inclusion the invariants of the different control points in $P_R$ (where $P_R$
is defined as in \ref{sec:compare_techniques}).
The detailed results are given in Table \ref{tab:domain}.

\JH{Commenter les resultats}

>>>>

For each program and each pair $(D_1,D_2)$ of abstract domains, we compare by
inclusion the invariants of the different control points in $P_R$ (where $P_R$
is defined as in \ref{sec:compare_techniques}).
The main results are given in Table \ref{tab:domain}.

Statistically, the domain of convex polyhedra gives the better results, but
regularly yields greater invariants than the domains of octagons/intervals.
Experiences shows is it mostly due to the widening operator.
The Octagon domain appears to be much better than intervals.
\JH{Commenter les resultats}

Analysis of linear equalities (PKEQ) performs very fast compared
to other abstract domains, but yields very unprecise invariants.
The comparison between the domain of convex polyhedra and linear congruences
shows the percentage of points where the use of congruences refines the
invariant. This is the case for $1.04\%$ of the control points in $P_R$.
